Combined Task and Motion Planner through an Interface Layer

### 2015-05-13 documentation/ps4.tex
made edits

We ran our test scenarios on the Baxter robot [Fig. \ref{fig:baxter}], designed by Rethink Robotics. 
Baxter is a humanoid robot with two 7 degree of freedom arms. 
Our tests used only the right arm with the two finger gripper.

@@

We present an interface between a task planner and motion planner [2]. 
Baxter executes a variety of tests to measure the performance of the interface layer. 
The tests demonstrate that the interface layer respects all of the geometric constraints. 
Baxter picks up objects in a reasonable order to avoid collisions.

The goal of the first test is to move the object at the center of a 3x3 square grid of objects to a goal surface. 
The goal of the second test is to sort red, green, and blue blocks into separate bins.
Figure \ref{fig:scenarios} shows the setup of the different test scenarios.

@@

Given that the pose generation and state update vary between domains, we implement domain specific pose generator class and state update function for the scenarios described in section \ref{tests}.

@@

\begin{figure}[h]
\centering
\def\svgwidth{0.5\textwidth}
\input{figures/blockDiagram.pdf_tex}
\caption{System Block Diagram\label{fig:blockDiagram}}
\end{figure}

@@

\subsection{Motion Planner}
We used the MoveIt! motion planner [3]. We implenented a ROS service wrapper for this off-the-shelf motion planner so as to comply with the API.
It takes as input the state of the world, the action to be performed, and a pose goal (i.e. a series of waypoints to perform the action).
MoveIt! is then used to instantiate motion plans between these waypoints. The motion planner service returns a boolean specifying the success/failure of the instantiation of the motion plan, the motion plan itself, and the updated world state (which can be unchanged if the action failed).

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{figures/figure4.png}
\caption{Illustration of the interface layer’s refinement process. 
Action arguments have been abbreviated. 
Taken from [2]
\label{fig:figure4}}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm1}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{figures/algorithm2}}
	\caption{Pseudo-code for the underlying algorithms of the interface layer. Taken from [2]\label{fig:algorithms}}
\end{figure}

We start with an initial state where no objects obstruct any motions.  
From there, we look for a high level plan.  
If we do succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.

@@

When the pose generator is called by the interface layer, it generates a set of random poses for each action. 
Each pose is made up of a set of waypoints.

For the PICKUP action, it generates the following waypoints: near the object and pointing towards it, touching the object, lifting the object, and a standard home position. 
The first waypoint is randomly generated and places the gripper about 15 centimeters away from the object.
We divided the set of possible random yaw angles around the object into several distinct ranges, called \textit{slices}. 
Each call to the pose generator generates a random angle in one of the ranges.
The second waypoint moves the arm so that the object is in the gripper. 
The third waypoint is in the exact same position with the gripper closed. 
The next waypoint is directly above the previous waypoint, high enough so that the object is above all of the other objects on the table. 
Finally, the last waypoint goes to the standard home position for the square grid task and moves  above the correct bin for the sorting task.

For the PUTDOWN action, the pose generator generates the following waypoints: above the target location, at the target location with the gripper closed, at the target location with the gripper open, 15 cm backed away from the target location, and the standard home position. 
The target location is randomly generated, but the pose generator checks to make sure that no objects are at or near the target location.

@@

This enables us to find plans a lot more quickly: whenever a plan is possible, we find it by backtracking search.  
Often, the first pose that's tried won't be viable but another pose will.  
Partial trajectory mode will only try the first pose before giving up and identifying blocking objects.
If partial trajectory mode is continually used, then often the plans created are much longer than necessary just because an invalid first pose is chosen when other options would have worked fine.
Using the full backtracking search on each new high level plan avoids this problem.

>>>>

We ran our test scenarios on the Baxter robot [Fig. \ref{fig:baxter}], designed by Rethink Robotics. 
Baxter is a humanoid robot with two 7 degree of freedom arms and a fixed based. 
Our tests used only the right arm with the two finger gripper.

@@

We present an interface between a task planner and a motion planner [2]. 
Baxter executes a variety of tests to measure the performance of the interface layer. 
The tests demonstrate that the interface layer respects all of the geometric constraints. 
Baxter picks up objects in a reasonable order to avoid collisions.

The goal of the first test is to move the object at the center of a $3\times3$ square grid of objects to a goal surface. 
In order to achieve the goal, Baxter must move some of the blocks surrounding the center block before placing the center block on the target surface.
The goal of the second test is to sort red, green, and blue blocks into separate bins.
For this task, the high level plan must ensure that Baxter does not try to pick up a block that is surrounded by other blocks.
Figure \ref{fig:scenarios} shows the setup of the different test scenarios.

@@

Given that the pose generation and state update vary between domains, we implement domain specific pose generator class and state update function for the scenarios described in Section \ref{tests}.

@@

\begin{figure}[h]
\centering
\def\svgwidth{0.7\textwidth}
\input{figures/blockDiagram.pdf_tex}
\caption{System Block Diagram\label{fig:blockDiagram}}
\end{figure}

@@

\subsection{Motion Planner}
We used the MoveIt! motion planner [3]. 
We implenented a ROS service wrapper for this off-the-shelf motion planner so as to comply with the API.
It takes as input the state of the world, the action to be performed, and a pose goal (i.e. a series of waypoints to perform the action).
MoveIt! is then used to instantiate motion plans between these waypoints. 
The motion planner service returns a boolean specifying the success or failure of the instantiation of the motion plan, the motion plan itself, and the updated world state (which can be unchanged if the action failed).

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{figure4}
\caption{Illustration of the interface layer’s refinement process. 
Action arguments have been abbreviated. 
Taken from [2]
\label{fig:figure4}}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\subfloat{\includegraphics[width=.45\linewidth]{algorithm1}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{algorithm2}}
	\caption{Pseudo-code for the underlying algorithms of the interface layer. Taken from [2]\label{fig:algorithms}}
\end{figure}

We start with an initial state where no objects obstruct any motions.  
From there, we look for a high level plan.  
If we succeed at finding a high level task plan, we begin the process of attempting to find a motion corresponding to each action.

@@

When the pose generator is called by the interface layer, it generates a set of random poses for each action. 
Each pose is made up of a set of waypoints. 
We generate multiple waypoints for an action to ensure that the motions avoid collisions.

For the PICKUP action, it generates the following waypoints: a pre-grasp near the object and pointing towards it, touching the object, grasping the object, lifting the object, and a standard home position. 
The pre-grasp is randomly generated and places the gripper about 15 centimeters away from the object.
We divided the set of possible random yaw angles around the object into several distinct ranges, called \textit{slices}. 
Each call to the pose generator generates a random angle in one of the ranges.
The second waypoint moves the arm so that the object is in the gripper. 
The grasping waypoint is in the exact same position with the gripper closed. 
The lifting waypoint is directly above the grasping waypoint, high enough so that the object is above all of the other objects on the table. 
Finally, the last waypoint goes to the standard home position.

For the PUTDOWN action, the pose generator generates the following waypoints: above the target location, a set down position with the gripper closed, a set down position with the gripper open, 15 cm backed away from the target location, and the standard home position. 
The target location is randomly generated, but the pose generator checks to make sure that no objects are at or near the target location.

@@

This enables us to find plans a lot more quickly: whenever a plan is possible, we find it by backtracking search.  
Often, the first pose that is tried will not be viable but another pose will.  
Partial trajectory mode will only try the first pose before giving up and identifying blocking objects.
If partial trajectory mode is continually used, then often the plans created are much longer than necessary just because an invalid first pose is chosen when other options would have worked fine.
Using the full backtracking search on each new high level plan avoids this problem.
